Linear response theory for core set identification

### 2012-07-26 writedown/linear.response/langevin.tex
fix bugs
add non-linear response

\subsection{General response theory for core set identification}

@@

@@

@@

  \Delta F_e^{i-1}(s)\,

@@

  \vect D(\vect q_s,\vect p_s)\cdot\dd\vect W_s
  [\Delta F_e^{i-1}(s)]^2\,

@@

  \vect D^2(\vect q_s,\vect p_s)\,\dd s

@@

  \vect D(\vect q_\eta,\vect p_\eta)\cdot\dd\vect W_\eta
  [\Delta F_e^{i-1}(t)]^2\,

@@

  \vect D^2(\vect q_\eta,\vect p_\eta)\,\dd \eta

@@

>>>>

\subsection{Higher orders response theory for core set identification}

@@

\begin{align}\label{eqn:pert-exact-1}

@@

  \\\label{eqn:pert-exact-2}

@@

@@

  \Delta F_e^{i-1}(s)\,\vect D(\vect q_s,\vect p_s)\cdot\dd\vect W_s

@@

  [\Delta F_e^{i-1}(s)]^2\,\vect D^2(\vect q_s,\vect p_s)\,\dd s

@@

  \Delta F_e^{i-1}(t)\,\vect D(\vect q_\eta,\vect p_\eta)\cdot\dd\vect W_\eta

@@

  [\Delta F_e^{i-1}(t)]^2\,\vect D^2(\vect q_\eta,\vect p_\eta)\,\dd \eta

@@

This is the exact result, from where we can develop
the response (also non-linear) theroy.
Before doing so, we should assume the perturbation can be expanded,
and well approximated in a finite dimensional space:
  F^i_e(t)
  \sum_{j = 1}^\infty
  s^i_j M_j(t)
with this expansion, we have
\begin{align}\label{eqn:exact-ratio-11}
  \sum_{j=1}^\infty
  \Delta s_j^{i-1}G_j[\vect X_s]
  \frac12 \sum_{j,k=1}^\infty
  \Delta s_j^{i-1} \Delta s_k^{i-1}H_{jk}[\vect X_s]
  \bigg\}\\\label{eqn:exact-ratio-21}
  G_0[\vect X_\eta]
  \frac12[\Delta F_e^{i-1}(t)]^2
  H_{00}[\vect X_\eta]
\begin{align}\label{eqn:Gj}
  G_j[\vect X_s]
  \frac 1\sigma
  M_j(s)\,\vect D(\vect X_s)\cdot\dd\vect W_s\\\label{eqn:Hjk}
  H_{jk}[\vect X_s]
  \frac 1{\sigma}
  M_j(s)\,M_k(s)\,\vect D^2(\vect X_s)\cdot\dd s
\begin{align}\label{eqn:G0}
  G_0[\vect X_\eta]
  \frac 1\sigma
  M_j(\eta)\,\vect D(\vect X_\eta)\cdot\dd\vect W_\eta\\\label{eqn:H00}
  H_{00}[\vect X_\eta]
  \frac 1{\sigma}
  M_j(\eta)\,M_k(\eta)\,\vect D^2(\vect X_\eta)\cdot\dd \eta
Notice that Eqn.~\eqref{eqn:Gj}--\eqref{eqn:H00} are perturbation
independent, therefore can be measured with the dynamics $i-1$.
Expanding \eqref{eqn:exact-ratio-11} and \eqref{eqn:exact-ratio-21}
up to $\mathcal O(\varepsilon^3)$ yields
\begin{align}\label{eqn:expan-ratio-1}
  \sum_{j=1}^\infty
  \Delta s_j^{i-1}G_j[\vect X_s]
  \frac12
  \sum_{j,k=1}^\infty
  \Delta s_j^{i-1} \Delta s_k^{i-1}H_{jk}[\vect X_s]
  \frac12  
  \sum_{j,k=1}^\infty
  \Delta s_j^{i-1}\Delta s_k^{i-1}G_j[\vect X_s]G_k[\vect X_s]
  \mathcal O(\varepsilon^3)
  \\\label{eqn:expan-ratio-2}
  1 +
  G_0[\vect X_\eta]
  \frac12[\Delta F_e^{i-1}(t)]^2
  H_{00}[\vect X_\eta]
  \frac12[\Delta F_e^{i-1}(t)]^2
  G_0[\vect X_\eta]
  \big\}^2
  \mathcal O(\varepsilon^3)
Therefore, by the expansion formula \eqref{eqn:expan-ratio-1} and
\eqref{eqn:expan-ratio-2}, the response theory for the
\eqref{eqn:pert-exact-1} and \eqref{eqn:pert-exact-2} can be
established.
